% $Id$

Installing the bootloader is only needed once. It simply requires you
to replace a file on your \dap{} with the Rockbox bootloader. To be able
booting the original firmware please make sure to rename the original file
properly. If you ever wish to uninstall Rockbox you should keep a backup copy
of the original file.

\begin{itemize}
\item Download the Rockbox bootloader from
  \url{http://download.rockbox.org/bootloader/gigabeat/}
\item Starting at the root directory of your player browse into the directory
  \fname{GBSYSTEM} and from that into the subdirectory \fname{FWIMG}.
  These directories are hidden. Make sure that you have configured your browser
  to show hidden files or you may be unable to see \fname{FWIMG}.
\item In that directory you'll find a file called \fname{FWIMG01.DAT}. This too
  may be hidden. Rename the file to \fname{FWIMG01.DAT.ORIG}. Make sure you
  spelled that name  correctly as it is needed for booting the \playerman{} firmware.
\item Now copy the file \fname{FWIMG01.DAT} you downloaded to that directory.
  Make sure the spelling is correct.
\end{itemize}

\warn{After installing the bootloader you \emph{need} to power-cycle the 
\dap{} by doing the following steps. Failure to do so may result in problems.}
\begin{itemize}
\item Eject / unmount USB drive and unplug the USB cable.
\item Unplug any power adapter.
\item Hold the \ButtonPower{} button to turn off the \dap{}.
\item Slide the battery switch located on the bottom of the \dap{} from 
    `on' to `off'
\item Slide the battery switch back from `off' to `on'
\end{itemize}
