\subsubsection{UMS and MTP}
The \playertype{} can be connected to a computer in two different modes:
\begin{itemize}
  \item Universal Mass Storage (UMS): In this mode, it will appear on your computer as a regular disk. This mode works with all major operating systems, including Windows, Linux and Mac OS X.
  \item Media Transfer Protocol (MTP): In this mode, it will appear on your computer as a Media Device. MTP was created by Microsoft for use with DAPs and only works with Windows XP and Media Player 10.
\end{itemize}
The \playerlongtype{} is \opt{h10}{only available as a MTP device, but}\opt{h10_5gb}{available as both a MTP and as a UMS device, depending on where and when you bought it. You can tell which you have by how it appears when you connect it to a computer. If it appears as a regular disk then it is UMS. If it appears as a Media Device on Windows XP, or if it doesn't appear at all on other operating systems, then it is MTP. Even if you have a MTP \dap{}, it} can be forced into UMS mode using the UMS trick.

\subsubsection{UMS mode and the UMS trick}
It is possible to force a MTP \playertype{} to start up in UMS mode using the following procedure:
\begin{enumerate}
  \item Ensure the \dap{} is fully powered off by \opt{h10}{using a pin to push the small reset button inside the hole between the Hold switch and remote control connector.}\opt{h10_5gb}{removing the battery and putting it back in again.}
  \item Connect your \playertype{} to the computer using the data cable.
  \item Hold \ButtonRight{} and push \ButtonPower{} to turn the \dap{} on.
  \item Continue holding \ButtonRight{} until the USB Connected screen appears.
  \item The \dap{} will now appear as a regular disk on your computer.
\end{enumerate}
\note{Once Rockbox has been installed, when you shut down your \dap{} from Rockbox it will totally power the player off so step 1 is no longer necessary.}

\subsubsection{Installation}
\begin{enumerate}
  \item Download 
  \opt{h10}{\url{http://download.rockbox.org/bootloader/iriver/H10_20GC.mi4}}
  \opt{h10_5gb}{
    \begin{itemize}
      \item \url{http://download.rockbox.org/bootloader/iriver/H10.mi4} if your \dap{} is UMS or
      \item \url{http://download.rockbox.org/bootloader/iriver/H10_5GB-MTP/H10.mi4} if it is MTP.
    \end{itemize}}
  \item Connect your \playertype{} to the computer using UMS mode and the UMS trick\opt{h10_5gb}{ if necessary}.
  \item Rename the \opt{h10}{\fname{H10\_20GC.mi4}}\opt{h10_5gb}{\fname{H10.mi4}} file to \fname{OF.mi4} in the \fname{System} directory on your \playertype{}.
    \opt{h10_5gb}{\note{If you have a Pure model \playertype{} (which doesn't have a FM radio) it is possible that this file will be called \fname{H10EMP.mi4} instead. If so, rename the \fname{H10.mi4} you downloaded in step 1 to \fname{H10EMP.mi4}.}}
    \note{You should keep a safe backup of this file for use if you ever wish to switch back to the \playerman{} firmware.}
    \note{If you can't see the \fname{System} directory, you will need to make sure your operating system is configured to show hidden files and directories.}

  \item Copy the \opt{h10}{\fname{H10\_20GC.mi4}}\opt{h10_5gb}{\fname{H10.mi4} (or \fname{H10EMP.mi4} if you have a \playertype{} Pure)} file you downloaded to the System directory on your \dap{}.
\end{enumerate}
