% $Id$ %
\chapter{Getting started}
\section{Welcome}
This is the manual for Rockbox. Rockbox is an open source firmware replacement
for a growing number of MP3 players. Rockbox aims to be considerably more
functional and efficient than your device's stock firmware while remaining easy
to use and customizable. Rockbox is written by users, for users. Not only is it
free to use, it's also released under the GNU public license, which means that
it will always remain free to both use and to change.

Rockbox has been in development since 2001, and recieves new features, tweaks
and fixes each day to provide you with the best possible experience on your MP3
player. A major goal of Rockbox is to be simple and easy to use, yet remain very
customizable and configurable. We believe that you should never need to go
through a series of menus for an action you perform frequently. We also believe
that you should be able to configure almost anything about Rockbox you could
want, pertaining to functionality. Another top priority of Rockbox is audio
playback quality -- Rockbox, for most models, includes a wider range of sound
settings than that device's original firmware. A lot of work has been put into
making Rockbox sound the best it can, and improvements are constantly being made.
All models have access to a large number of plugins, including many games,
applications, and graphical ``demos''. You can load different configurations
quickly for different purposes (e.g. a large font for in your car, different
sound settings for at home). Rockbox features a very wide range of languages, and
all supported models also have the ability to talk to you -- menus can be voiced
and filenames spelled out or spoken.

\section{Getting more help}
This manual is intended to be a comprehensive introduction to the Rockbox
software. There is, however, more help available.  The Rockbox website at
\url{http://www.rockbox.org/} contains very extensive documentation and guides
written by members of the Rockbox community and this should be your first port
of call when looking for further help.

\section{Installing Rockbox}\label{sec:installing_rockbox}
\opt{MASCODEC}{
  \subsection{Using the windows installer}
  Using the Windows self installing executable to install Rockbox is the easiest
  method of installing the software on your Jukebox.  Simply follow the
  on-screen instructions and select the appropriate drive letter and Jukebox
  model when prompted.  You can use ``Add / Remove Programs'' to uninstall the
  software at a later date.

  \subsection{Manual installation}
  For non{}-Windows users and those wishing to install manually from the archive
  the procedure is still fairly simple.
}
\opt{SWCODEC}{
\subsection{Introduction}
There are two separate components of Rockbox that need to be installed in order
to run Rockbox.
\begin{enumerate}
\item The Rockbox bootloader. This is the component of Rockbox that is installed
  to the flash memory of your \playerman. The bootloader is the program that tells
  your \dap\ how to boot and load other components of Rockbox.
\item The Rockbox firmware. Unlike the \playerman\ firmware, which runs entirely
  from flash memory, most of the Rockbox code is contained in the build that
  resides on your jukebox's hard drive. This makes it easy to update Rockbox. The
  build contain a file named \firmwarefilename\ and a directory called
  \fname{.rockbox} which are located in the root directory of your  hard drive.
\end{enumerate}
\opt{h1xx,h300}{\input{getting_started/iriver_install.tex}}
\opt{ipod4g,ipodcolor,ipodnano,ipodmini,ipodvideo}
	{\input{getting_started/ipod_install.tex}}
\opt{x5}{\input{getting_started/iaudio_install.tex}}
   
  \subsection{Installing the firmware}
  After installing the bootloader the installation becomes fairly easy.
}

Connect your \playername\ to the computer via USB as described in the 
manual that came with your \playername. On Windows, the \playername\ drive 
will appear as a drive letter in your ``My Computer'' folder. Take the file 
that you downloaded above, and unpack its contents to your \playername\ drive.
You can do this using a program such as \url{http://www.info-zip.org/} or 
\url{http://www.winzip.org/}.

You will need to unpack all of the files in the archive onto your hard disk. If 
this has been done correctly, you will have a file called 
\fname{\firmwarefilename} in the main folder of your \playername\ drive, and
also a folder called /\fname{.rockbox}, which contains a number of system files
used by the software.
\note{Please note that the firmware folder starts with a leading dot. You may
experience problems when trying to create such folders when using Windows.
Directly unzipping to your \dap's drive works flawlessly; it is only Windows'
Explorer that is limited in handling such files.}

\section{Enabling Speech Support (optional)}\label{sec:enabling_speech_support}
If you wish to use speech support you will also need a language file, available
from \url{http://www.rockbox.org/twiki/bin/view/Main/VoiceFiles/}.  For the
English language, the file is called \fname{english.voice}. When it has been
downloaded, unpack this file and copy it into the \fname{lang} folder which is
inside the /\fname{.rockbox} folder on your Jukebox. Voice menus are turned on
by default. See page \pageref{ref:Voiceconfiguration} for details on voice
settings.

\section{Running Rockbox}
Remove your Jukebox from the computer's USB port. Unplug any connected power
supply and turn the unit off. When you next turn the unit on, the Jukebox
firmware will start to load, and then it will load Rockbox for you. When you see
the Rockbox splash screen, Rockbox is loaded and ready for use.

\section{Uninstalling Rockbox}
If you would like to go back to using the original \playername\ software, then
connect the \playername\ to your computer, and delete the
\fname{\firmwarefilename} file. If you wish to clean up your disk, you may also
wish to delete the \fname{.rockbox} folder and its contents. Turn the
\playername\ off and on and the normal \playername\ software will load.

\section{Updating Rockbox}
The latest release of the Rockbox software will always be available from
\url{http://www.rockbox.org/download/}.
\opt{MASCODEC}{
  Windows users may wish to download the self-extracting Windows installer,
  which works for all Jukebox models, but those wishing to install manually or
  using a different operating system should choose the .zip archive containing
  the firmware for their model of the Jukebox.
}