\subsection{Announce Status}

The \setting{Announce Status} plugin allows you to use the voice system to announce things in the audio stream

Currently the list includes:
\begin{itemize}
\opt{rtc}{
\item Time
\item Date
  }
\item Track name (spelled)
\item Artist name (spelled)
\item Track Elapsed / Remaining
\item Playlist position
\item Battery level
\item Sleep Timer remaining
\item Running time
\end{itemize}

\subsubsection{Configuration}
The input for announce format is actually a parsed string of options
while you can edit the items directly to get your preferred order preset options are included.
If you choose to manually edit the option string the input box helpfully has all valid options for the parser

\opt{rtc}{
\setting{TIME}
\begin{itemize}
\item DT current time
\item D1 'time'
\item DD current date
\item D2 'date'
\end{itemize}
}

\setting{TRACK}
\begin{itemize}
\item TT title (spelled)
\item TA artist (spelled)
\item TE elapsed
\item TL length
\item TR remaining
\item T1 'elapsed'
\item T2 'remaining'
\item T3 'of'
\end{itemize}

\setting{PLAYLIST}
\begin{itemize}
\item PC current track
\item PN total tracks
\item PR remaining tracks
\item P1 'track'
\item P2 'of'
\end{itemize}

\setting{BATTERY}
\begin{itemize}
\item BP level (percentage 0-100)
\item BM remaining time (HMS)
\item B1 'battery level'
\end{itemize}

\setting{SLEEPTIMER/RUNTIME}
\begin{itemize}
\item RT runtime (HMS)
\item R1 'running time'
\item RS sleep timer remaining (HMS)
\item R2 'sleep time'
\item R3 'remaining'
\end{itemize}

\subsubsection{Usage}
\begin{description}
\item [Timeout] [0-360] seconds announcements will not repeat until timeout is met.
\item [Announce on] [Off, Track Change].
\item [Grouping] [0-7] 0- play all, 1-7 only announce the first n items.
                Helpful for infrequently used items.
\item [Announcement format] Select from preset options or manually enter your own.
\item [Quit] Exit without Saving.
\item [Save and Exit] Save settings and exit
\end{description}

Now that we have configuration out of the way (don't forget the preset options if this looks daunting)

Not quite out of the woods yet though...

You can choose to get announcements each track change or only when you run the plugin again
it would get quite annoying to have to go run the plugin every time you wanted a status update though

Enter the \setting{WPS Hotkey}
now we will assign the wps hotkey to announce\_status
Settings>General Settings>What's Playing Screen>WPS Hotkey
choose 'OpenPlugin' browse to 'demos'
finally choose 'announce\_status'

Now you should be able to press your wps hotkey and get status updates on command.

\note{
This is actually a plugin running on top of the WPS screen and as such running other plugins stops the announce plugin
so if you only choose the track change option you should probably set the announce plugin to open on startup and keep
in mind that you may have to start the plugin again later.}
