\subsection{Countdown Timer}

A countdown timer. Set the desired duration, start the countdown, and the
\dap{} will alert you with a beep sequence when time is up. The timer
defaults to 10 minutes on launch.

\subsubsection{Setting the timer}

When the plugin starts, the display shows the time to count down from with
the active field highlighted in brackets (e.g. \texttt{[10]:00}).

\begin{btnmap}
    \opt{scrollwheel}{\PluginScrollFwd{} / \PluginScrollBack{} or }
    \PluginUp{} / \PluginDown
       \opt{HAVEREMOTEKEYMAP}{& \PluginRCUp{} / \PluginRCDown}
    & Increase / decrease the selected field \\

    \PluginLeft{} / \PluginRight
       \opt{HAVEREMOTEKEYMAP}{& \PluginRCLeft{} / \PluginRCRight}
    & Switch between the minutes and seconds fields \\

    \PluginSelect
       \opt{HAVEREMOTEKEYMAP}{& \PluginRCSelect}
    & Start the countdown \\
\end{btnmap}

Minutes can be set from 0 to 99 and seconds from 0 to 59. The timer cannot
be started if both fields are zero. Values wrap around when incremented or
decremented past their limits.

\subsubsection{Running the timer}

Once started, the remaining time counts down in \texttt{MM:SS} format.

\begin{btnmap}
    \PluginSelect
       \opt{HAVEREMOTEKEYMAP}{& \PluginRCSelect}
    & Pause / resume the timer \\

    \nopt{IPOD_4G_PAD,IPOD_3G_PAD}{\PluginCancel}
    \opt{IPOD_4G_PAD,IPOD_3G_PAD}{\ButtonMenu}
       \opt{HAVEREMOTEKEYMAP}{& \PluginRCCancel}
    & Quit (only available while paused) \\
\end{btnmap}

When the countdown reaches zero the \dap{} pauses playback, turns on the
backlight, and plays three beeps. After the alert the timer continues
running into overtime, displaying the elapsed overtime as
\texttt{-MM:SS}. Playback resumes automatically after the beep sequence.
The timer can be quit by pausing it and pressing the quit button.
