% $Id$ %
\subsection{Disk Tidy}
  Disk Tidy deletes junk files commonly left behind by Windows, Linux and
  OS X after connecting your \dap{} over USB. Select the files you want to
  delete in the ``Files to Clean'' menu and select ``Start Cleaning'' to begin
  the process. The settings are stored in the plain text file
  \fname{.rockbox/rocks/apps/disktidy.config} that is user-modifiable to allow
  custom entries to be added.
  
  The asterisk character (``*'') can be used as a wild-card which will match any
  string; however only the first asterisk will be recognised as a wild-card 
  with any additional uses being taken as literal.\\*
  
  \warn{Be careful when you use custom entries as you could accidentally delete
        important files.}

  \subsubsection{Available Options}
  \begin{description}
    \item[All] selects all Linux, OS X, and Windows files.
    \item[None] deselects all file options.
    \item[Linux] selects Linux files. Default files are
      \fname{.dolphinview}, \fname{.d3lphinview}, and \fname{.Trash-*/}.
    \item[Windows] selects Windows files. Default files are
      \fname{Thumbs.db}, \fname{$RECYCLE.BIN/}, \fname{Desktop.ini}, \fname{Recycled/} and
      \fname{System Volume Information/}.
    \item[Mac] selects OS X files. Default files are \fname{.\_*}, \fname{.DS\_Store},
      \fname{.Spotlight-V100/} and \fname{.Trashes/}.
    \item[Other] selects additional files added to the configuration file by the
                 user.
  \end{description}
  
  \begin{btnmap}
      \ActionStdCancel
        \opt{HAVEREMOTEKEYMAP}{& \ActionRCStdCancel}
      & Exit / Abort\\
  \end{btnmap}
