\subsection{Superdom}

Superdom is a turn based strategy game, where the aim is to defeat the computer
player by overpowering them using your army.

When the game starts the player is given roughly 50% of the tiles on the map,
two farms, and two factories. To overpower the enemy, you must place resources
in adjacent tiles (diagonals do not count), such that your strength is greater
than the computers, then attack the square.

Each ``year'' is broken up into three phases: purchasing, movement, and war.
During the purchasing phase you are allocated money and food, may purchase
units/buildings, and may access the bank.

During the movement phase you can move your units only to adjacent squares
(except planes, which may move anywhere), at a cost of 1 move per unit you move.
(Men are considered to be one unit, no matter how many you move). You can change
the number of moves you receive by default in the settings, and you may purchase
additional moves for \$100 each. You may also launch nuclear weapons if you have
purchased any.

During the war phase you can attack the enemy. This is where the strengths come
into play. Each tile has its own strength for both the computer, and the human
player. If you attack a square owned by the computer player where your strength
is greater than the computer's, you will win the tile -- and take control of any
building that were on it. If the strengths are equal, a victor is chosen at
random.

The bank (in the purchasing phase) is a place where you can store your money
and earn interest (usually about 10% p.a.), however, while the money is in the
bank, it is not accessible until the next purchasing phase.

\subsubsection{Notes on food}
Each year you are allocated an amount of food based on the number of farms you
control. Food is used to feed your men, but if you do not have enough food to
feed your population of men, some will die of starvation.

\subsubsection{Summary of units}
\begin{table}
    \begin{rbtabular}{\textwidth}{lccX}%
        {\textbf{Unit} & \textbf{Cost} & \textbf{Individual strength}%
         & \textbf{Special abilities}}{}{}
        Men       & \$1 each & 1.33 per 100 & No square population limit, however %
                                              require 1 food each per year\\
        Tanks     & \$300    & 3 & None\\
        Planes    & \$600    & 4 & Can move to any human controlled point on the map\\
        Farms     & \$1150   & 3 & Generates additional food at start of year\\
        Factories & \$1300   & 3 & Generates additional food at start of year\\
        Nukes     & \$2000   & 2 & During the movement phase you may lauch a nuke %
                                   to destroy all units on a given tile\\
    \end{rbtabular}
\end{table}
Also note that the colour of the adjacent tiles also count towards your strength.
