\subsection{\label{sec:text_editor}Text Editor}
This plugin allows you to view and edit simple text documents on your DAP.
You can view files by using \setting{Open with} from the
\setting{Context Menu} (see \reference{ref:Contextmenu}).

\subsubsection{Usage}
If you start the Text Editor from the plugin browser you will be greeted with
a blank screen. When started from the \setting{Open with} menu item your file 
should be shown on the screen. You can now edit the file.
The Text Editor is line based. This means you can edit one line at a time using
the \setting{Virtual Keyboard} (see \reference{sec:virtual_keyboard}).

\begin{itemize}
  \item Move the selection bar to the line you want to edit.
  \item Edit the highlighted text line or insert a new one using the Item Menu.
  \item When finished editing exit the Text Editor. You'll be shown a list of
        save options. 
\end{itemize}
\note{When you have not changed the file the Text Editor will quit immediately.}

\begin{btnmap}
    \ActionStdOk 
      \opt{HAVEREMOTEKEYMAP}{& \ActionRCStdOk}
    & Edit Line / Select Character\\

    \ActionStdCancel 
      \opt{HAVEREMOTEKEYMAP}{& \ActionRCStdCancel} 
    & Exit / Abort Editing\\

    \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ActionStdContext}
    \nopt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ActionStdMenu}
      \opt{HAVEREMOTEKEYMAP}{& \ActionRCStdMenu} 
    & Show Item Menu\\

    \nopt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{
        \ActionStdContext
          \opt{HAVEREMOTEKEYMAP}{& \ActionRCStdContext}
        & Delete Line\\
    }
\end{btnmap}

