% $Id:$ %
\section{\label{ref:PlaylistOptions}Playlists}

The \setting{Playlists} submenu allows you to configure settings
related to playlists.


\begin{description}

\item[Playlist Viewer Settings.]
   This submenu contains settings related to the Playlist Viewer.
   \begin{description}
    \item[Show Icons.] This toggles display of the icon for the currently
    selected playlist entry and the icon for moving a playlist entry
    \item[Show Indices.] This toggles display of the line numbering for
       the playlist
    \item[Track Display.] This toggles between filename only and full path
       for playlist entries
  \end{description}

\item[Recursively Insert Directories.]
  If set to \setting{On}, then when a directory is inserted or queued into a
  dynamic playlist, all subdirectories will also be inserted. If set to \setting{Ask},
  Rockbox will prompt the user about whether to include sub-directories.

\item[Current Playlist.]
  This submenu contains settings related to the current dynamic playlist.
  \begin{description}

  \item[Warn When Erasing Dynamic Playlist.]
  If set to \setting{Yes}, Rockbox will provide a warning if the user attempts to
  take an action that will cause Rockbox to erase the current dynamic playlist.

  \item[Keep Current Track When Replacing Playlist.]
  If set to \setting{Yes}, then \setting{Play} and \setting{Play Shuffled} in
  the \setting{Current Playlist submenu} will allow the current track to finish
  playing before the new tracks play. If set to \setting{No}, the current
  track will be interrupted and new tracks will start playing immediately.

  \item[Show Shuffled Adding Options.]
  If set to \setting{No}, Rockbox will not offer to add shuffled tracks
  in the \setting{Current Playlist submenu}.

  \item[Show Queue Options.]
  If set to \setting{No}, Rockbox will not display the options to queue items in
  the \setting{Current Playlist submenu}.
  If set to \setting{In Submenu}, Rockbox will move the options into a
  separate submenu.

  \item[Reload After Saving.]
  If set to \setting{Yes}, saving the current playlist from the While Playing Screen's
  Context Menu will cause Rockbox to load the newly saved playlist and resume it to the
  current position. This is useful for creating bookmarks after modifying or customizing
  a playlist. Saving playlists outside of the While Playing Screen's Context Menu will
  not be affected by this setting.

  \end{description}

\end{description}
