% $Id$ %

\section{\label{ref:StartupShutdownOptions}Startup/Shutdown}

The \setting{Startup/Shutdown} sub menu allows you to configure items which
are run at startup, or initiate a shutdown when conditions are met.

\begin{description}
    \item[Show Shutdown Message.] If set, a message will be displayed and the display
    will light up before the device shuts down.
\end{description}

\subsection{Start Screen}
  Set the screen that Rockbox will start in. The default is the main menu but
  the following options are available:
  % almost all items in the main menu with a few exceptions
  \begin{description}
    \item[Previous Screen.] Start Rockbox in the same screen as when it was
    shut off.
    \item[Main Menu.] Show the main menu.
    \item[Files.] Display the file browser, starting in the root directory of
    your \dap.
    \item[Database.] Show the default database view.
    \item[Resume Playback.] Go to the WPS and and resume playback from where
    it was before turning off (if there is a playlist to resume).
    \item[Settings.] Display the main settings menu.
    \opt{recording}{
      \item[Recording.] Start the \dap{} in the recording screen
      (recording does not start automatically).
    }
    \opt{radio}{
      \item[FM Radio.] Go to the radio screen and start playing.
    }
    \item[Recent Bookmarks.] Show the list of recent bookmarks as
      described in \reference{ref:Bookmarkconfigactual}. Bookmarking needs
      to be enabled.
  \end{description}

\opt{clear_settings_on_hold}{
  \opt{ipod}{
    \subsection{\label{ref:ClearOnHold}Hold switch clears settings on startup }
      This option controls whether Rockbox clears its configuration if the hold
      switch is enabled during startup.

      \begin{description}
        \item[Yes.]
              Clear the settings if the hold switch is enabled during startup.
        \item[No.]
              Do not clear the settings, regardless of the hold switch's position.
        \end{description}
  }
  \nopt{ipod}{
    \opt{GIGABEAT_S_PAD}{
      \subsection{\label{ref:ClearOnHold}BUTTON A clears settings on startup }
        This option controls whether Rockbox clears its configuration if BUTTON_A
 is held during startup.
        \begin{description}
          \item[Yes.]
                Clear the settings if the BUTTON A is held.
          \item[No.]
                Do not clear the settings, regardless of BUTTON A.
          \end{description}
    }
    \nopt{GIGABEAT_S_PAD}{
      \subsection{\label{ref:ClearOnHold}BUTTON REC clears settings on startup }
        This option controls whether Rockbox clears its configuration if BUTTON REC
 is held during startup.
        \begin{description}
          \item[Yes.]
                Clear the settings if the BUTTON REC is held.
          \item[No.]
                Do not clear the settings, regardless of BUTTON REC.
          \end{description}
    }
  }
}

\subsection{\label{ref:IdlePoweroffSetting}Idle Poweroff}
  Rockbox can be configured to turn off power after the unit has been idle for
  a defined number of minutes. The \dap{} is idle when playback is stopped or
  paused. It is not idle while the USB or charger is connected
  \opt{recording}{, or while recording}.
  Settings are either \setting{Off} or 1 to 10 minutes in 1 minute steps. Then
  15, 30, 45 or 60 minutes are available.

\subsection{Sleep Timer}
  The \setting{Sleep Timer} powers off your \dap{} after a given time, whether
  playing or not.
  \begin{description}
    \item[Start Sleep Timer (\emph{duration}):]
      Shown when the \setting{Sleep Timer} is inactive, this option will
      initiate a \setting{Sleep Timer} with the duration shown in brackets.
    \item[Cancel Sleep Timer (\emph{remaining}):]
      Shown when the \setting{Sleep Timer} is active, this option will cancel
      the current \setting{Sleep Timer}.\\
      The time remaining before completion is shown in brackets.
    \item[Default Sleep Timer Duration:]
      The default number of minutes a new \setting{Sleep Timer} will run
      for.\\
      The values range from 5 minutes to 5 hours in 5 minute steps.\\
      If a timer is currently active, the timer's duration will be set to the
      newly entered value.\\
      The value set is persistent, see \reference{ref:config_file_options}.
    \item[Start Sleep Timer On Boot:]
      If set, a \setting{Sleep Timer} will be initiated when the device
      starts.
    \item[Restart Sleep Timer On Keypress:]
      If set, when a \setting{Sleep Timer} is active and a key is pressed, the
      \setting{Sleep Timer} will be restarted with the initial duration.
  \end{description}
