% $Id$ %
\section{\label{ref:SystemOptions}System}

\nopt{sansa,fuzeplus}%will probably be there on Sansas one day -  exclude it the simple way without specific option
{\nopt{sansaAMS}{
  \subsection{Battery}
  Options relating to the battery
  in the \dap.
  \begin{description}
    \item [Battery Capacity.] This setting can be used to tell Rockbox what
      capacity (in mAh) the battery being used has. The default is
      \opt{vibe500}{1000~mAh}%
      \opt{iriverh100,iriverh300}{1300~mAh}%
      \opt{mpiohd200}{850~mAh}%
      \opt{ipodmini}{400~mAh (1G) or 630~mAh (2G)}%
      \opt{ipodcolor}{700~mAh}%
      \opt{ipodnano}{300~mAh}%
      \opt{ipodvideo}{400~mAh (30~GB) or 600~mAh (60~GB and 80~GB)}%
      \opt{ipod4g}{630~mAh}%
      \opt{ipod3g}{630~mAh}%
      \opt{ipod1g2g}{1200~mAh}%
      \opt{iaudiom3,iaudiom5,iaudiox5}{950~mAh}%
      \opt{gigabeatf}{2000~mAh}%
      \opt{gigabeats}{700~mAh}%
      \opt{cowond2}{1600~mAh}%
      \opt{mrobe100}{720~mAh}%
      \opt{samsungyh920,samsungyh925}{900~mAh}%
      \opt{samsungyh820}{650~mAh}%
      \opt{xduoox3}{2000~mAh}%
      , which is the capacity value for the standard battery shipped with the \dap.
        Rockbox uses this value for runtime estimation, not battery percentage
        calculation. Changing this setting has no effect whatsoever on
        actual battery life. This setting only affects the accuracy of the
        runtime estimation as shown on screen.
      \opt{iaudiom3,iaudiom5,iaudiox5}{Rockbox does not automatically distinguish
        between the ``L'' models and the ``simple'' models which determine the
        default value. If your \dap{} is an
            \opt{iaudiom3}{M3L}%
            \opt{iaudiom5}{M5L}%
            \opt{iaudiox5}{X5L}
        set the value to 2250~mAh for more accuracy in the runtime estimation.}
      \opt{ipod,sansa}{This value is fairly meaningless in the \playerman{}
        family at present, and work is on-going into finding a better way to
        determine battery life.}

      \opt{battery_types}{
      \item [Battery Type.] This setting tells Rockbox which type of battery
        is currently used in the \dap{}.
       \nopt{xduoox3}{The two supported battery types are ``Alkaline'' or ``NiMH''.}
       \opt{xduoox3}{Older \playerman{} \playertype{} units shipped with a 1500mAh battery, while newer units ships with a 2000mAh battery.  If you are not sure which type you have, older units have a button marked ``ESC''.}
	}

      \opt{usb_charging_enable}{
      \item [Charge During USB Connection.] This option lets you control whether
        the \dap{} should charge during the USB connection and hence draw the
        full 500~mA. Turning it \setting{Off} is recommended if the \dap{} is
        connected through an unpowered USB hub or a laptop port. To use a USB
        AC adapter, select \setting{Force} to instruct the \dap{} to also
        charge when USB power is available but no connection is established.
      }

     \end{description}
}}
\opt{dircache,HAVE_DISK_STORAGE}{
\subsection{Disk}
    Options relating to the hard disk.

  \begin{description}
    \opt{HAVE_DISK_STORAGE}{
    \item [Disk Spindown.] Rockbox has a timer that makes it spin down the
      hard disk after it is idle for a certain amount of time. This setting
      controls the amount of time between the last user activity and the time
      that the disk spins down. This idle time is only affected by user
      activity, like navigating through the \setting{File Browser}. When the
      hard disk spins up to fill the audio buffer, it automatically spins down
      afterwards.
    }

    \opt{dircache}{
    \item [Directory Cache.] Rockbox has the ability to cache the contents of
      your drive in RAM. The \setting{Directory Cache} takes a small amount of
      memory away from Rockbox that would otherwise be used to buffer music,
      but it speeds up navigation in the file browser by eliminating
      the slight pause between the time a navigation button is pressed and the
      time Rockbox responds. Turning this setting on activates the
      directory cache, and turning it off deactivates the directory
      cache.
      \note{The first time you enable the directory cache,
      Rockbox will request a reboot of the \dap{} and upon restarting take a few
      minutes to scan the drive. After this, the directory cache will work in the
      background.}
    }
  \end{description}
} % \opt{dircache,HAVE_DISK_STORAGE}

\subsection{Limits}
This sub menu relates to limits in the Rockbox operating system.
  \begin{description}
    \item [Max Entries in File Browser.] This setting controls the limit on
    the number of files that you can see in any particular directory in the
    file browser. You can configure the size to be between 50 and
    10,000 files in steps of 50. The default is 400. Higher values will shorten
    the music buffer, so you should increase this setting \emph{only} if you have
    directories with a large number of files.

    \item [Max Playlist Size.] This setting controls the maximum size of
    a playlist. The playlist size can be between 1,000 and 32,000 files,
    in steps of 1,000 (default is 10,000). Higher values will shorten the
    music buffer, so you should increase this setting \emph{only} if you
    have very large playlists.

    \item [Glyphs To Cache.] This sets the default memory allocation size
    for fonts in unique glyphs. This should be set to the number of unique
    language glyphs and punctuation marks that are frequently displayed.
    The default is 250.
  \end{description}
  \note{You will need to restart your player for changes to \setting{Max
    Entries in File Browser} or \setting{Max Playlist Size} to take effect
    while \setting{Glyphs To Cache} will affect the next font load.}
% TODO: this needs to be rewritten in another style, it lets you mix sound from another source into the music
  \subsection{Line In} This option activates the line-in port on \dap, which is
    off by default. This is useful for such applications as:
    \begin{itemize}
    \item Game boy $\rightarrow$ \dap $\rightarrow$ human
    \item laptop $\rightarrow$ \dap $\rightarrow$ human
    \item LAN party computer $\rightarrow$ \dap $\rightarrow$ human
    \end{itemize}
\opt{quickscreen}{
  \subsection{Use Shortcuts Menu Instead of Quick Screen} This option
  activates the shortcuts menu instead of opening the quick screen when enabled.
}
\opt{HAVE_CAR_ADAPTER_MODE}{
\subsection{Car Adapter Mode}
      This option turns \setting{On} and \setting{Off} the car ignition
      auto stop function.
  \begin{description}
  \item [Car Adapter Mode.] When using the \dap{} in a car,
  \setting{Car Adapter Mode} automatically stops playback on the \dap{} when
  power (i.e. from cigarette lighter power adapter) to the external DC in jack
  is turned off. If the \setting{Car Adapter Mode} is set to \setting{On},
  Rockbox will pause playback when the external power off condition is
  detected. Rockbox will then shutdown the \dap{} after the length of time set
  in the \setting{Idle Poweroff} setting
  (see \reference{ref:IdlePoweroffSetting}).
  If power to the DC in jack is turned back on before the \emph{Idle Poweroff}
  function has shut the \dap{} off, playback will be resumed after
  \setting{Car Adapter Mode Delay} seconds after the power is applied.
  This delay is to allow for the time while the car engine is being started.
  \end{description}

  Once the \dap{} is shut off either manually, or automatically with the
  \setting{Idle Poweroff} function, it must be powered up manually to resume
  playback.

\subsection{Car Adapter Mode Delay}
  This option specifies
  the time between power being applied and playback resuming
  \begin{description}
  \item [Car Adapter Mode Delay.]  As different car headunits take
    varying amounts of time to start up, the \setting{Car Adapter Mode Delay}
    is configurable between 5 and 30 seconds, in 5 second increments.
  \end{description}
}

\opt{accessory_supply}{
\subsection{\label{ref:AccessoryPowerSupply}Accessory Power Supply}
This option turns the accessory power supply \setting{On} and \setting{Off}.
The Apple accessory protocol has been partially implemented in Rockbox, and
thus there is a reasonable chance that your favourite accessory will work.
The accessory may require power from the \dap{} to function, and if so you should turn
this option \setting{On}. If it is not required, then turning this setting
\setting{Off} will save battery and therefore result in better runtime.
}

\opt{lineout_poweroff}{
\subsection{\label{ref:LineoutOnOff}Line Out}
This option turns the \dap{}'s line-out \setting{On} and \setting{Off}. On some
devices an enabled line-out will consume some power even if not used. If it is
not required, then turning this setting \setting{Off} will save battery and
therefore result in better runtime.
}

\opt{HAVE_BUTTON_LIGHTS}{
  \opt{e200,e200v2}{
  \subsection{Wheel Light Timeout}
    This setting controls the amount of time the wheel lights shine after a
    button press or wheel turn. If set to \setting{Off}, the LEDs will not
    light when a button is pressed. If set to \setting{On}, the lights will
    never shut off. If set to a time (1 to 120 seconds), the wheel will stay
    lit for that amount of time after a button press or wheel turn.
  }
  \nopt{e200,e200v2}{
  \subsection{Button Light Timeout}
    This setting controls the amount of time the button lights shine after a
    button press. If set to \setting{Off}, the LEDs will not light when a
    button is pressed. If set to \setting{On}, the lights will never shut off.
    If set to a time (1 to 120 seconds), the buttons will stay lit for
    that amount of time after a button press.
  }
  \opt{gigabeatf}{
    \subsection{Button Light Brightness}
      Changes the brightness of the button lights.
  }
}

\subsection{Keyclick}
  This menu controls key clicks on button presses.
  \begin{description}
  \opt{hardware_click}{
    \item [Headphone Keyclick. ]This setting controls how strong the keyclicks
      played through the headphones are. If set to \setting{Off}, the keyclicks
      will be disabled.
    \item [Speaker Keyclick. ]This setting turns playing of keyclicks through
      the built in speaker \setting{On} or \setting{Off}.
  }
  \nopt{hardware_click}{
    \item [Keyclick. ]This setting controls how strong the keyclicks are.
      If set to \setting{Off}, the keyclicks will be disabled.
  }
  \item [Keyclick repeats.] This setting turns keyclick repeats \setting{On}
    and \setting{Off}. If set to \setting{On}, the keyclicks will be
    repeated when you hold down a button. If set to \setting{Off}, you will
    hear only one click.
  \end{description}

\opt{touchpad}{
  \subsection{Touchpad}
    These settings control the functions of touchpad devices.
    \begin{description}
    \opt{SANSA_FUZEPLUS_PAD,GIGABEAT_PAD}{
      \item [Touchpad Sensitivity. ]This setting controls the amount of pressure needed to
      register a touchpad press. If set to \opt{SANSA_FUZEPLUS_PAD}{\setting{25}}\opt{GIGABEAT_PAD}
      {\setting{High}} the lightest touch will register. If set to \opt{SANSA_FUZEPLUS_PAD}
      {\setting{-25}}\opt{GIGABEAT_PAD}{\setting{Normal}} a firmer press will be needed to register
      on the touchpad.
    }
    \end{description}
    \begin{description}
    \opt{touchpad_deadzone}{
      \item [Touchpad Deadzone. ]This setting controls the size of a configurable deadzone
      where touch events between virtual keys are ignored.  If set to \opt{SANSA_FUZEPLUS_PAD}
      {\setting{0}} there is effectively no deadzone. If set to \opt{SANSA_FUZEPLUS_PAD}
      {\setting{100}} the deadzones between each virtual button are set to a maximuim
      400px.
    }
    \end{description}
}




\nopt{hold_button}{
  \subsection{Advanced Key Lock}
    This option allows users to select actions that when within WPS or FMS will \emph{not} be
    blocked by the key lock (software hold switch).


        \begin{description}
        \item[Enabled.]
        Enables/disables the feature.

        \item[Settings.]
        Allows to select actions that will \emph{not} be blocked by the key lock.
                \begin{itemize}
                \item[Volume.]
                Volume up/down.
                \item[Play.]
                Toggling Play/Pause.
                \item[Seek.]
                Seeking in a track.
                \item[Skip.]
                Skipping of a track.
                \opt{HAVE_BACKLIGHT}{
                \item[Autolock On.]
                When the backlight turns off, softlock will lock the screen,
                activates when you press the lock key and if you manually lock
                again, while active it then disables autolock.
                \begin{itemize}
                        \item
                        (Lock Button Pressed \#1) >Auto Lock On
                            (device still unlocked till backlight timeout).
                        \item
                        (Lock Button Pressed \#2) >Auto Lock Off (device locked).
                        \item
                        (Lock Button Pressed \#3) >(device unlocked).
                \end{itemize}
                } %\opt{HAVE_BACKLIGHT}
                \opt{touchpad}{
                \item[Disable Touch.]
                 Blocks touch screen buttons like the original.
                }
                \item[Disable Notify.]
                Suppresses the notification 'Buttons Locked'
                    (still will if power button is pressed).
                \note{This is a pre-requisite for \setting{selectivebacklight}
                \reference{ref:selectivebacklight} to work also during key lock.}

                \end{itemize}
        Selected actions are indicated by a leading +.
        Note: If all options get de-selected, the entire feature is disabled.

        \end{description}
} %\nopt{hold_button}


\opt{usb_hid}{
  \subsection{\label{ref:USB_HID}USB HID}
    This option turns the USB HID feature \setting{On} and \setting{Off}.
    When this feature is enabled, the \dap{} enumerates as a Human Interface
    Device (HID), composed of several HID sub devices.
    Since the \dap{} also enumerates as a Mass Storage Device, it becomes a USB
    Composite Device, which contains both these devices.

  \subsection{USB Keypad Mode}
    This setting control the keypad mode when the \dap{} is attached to a
    computer through USB. Pressing a key on the \dap{} sends a keystroke the
    computer the \dap{} is attached to, according to the mapping set by the
    keypad mode. There are different modes which provide different
    functionality.
    \opt{SANSA_E200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD%
        ,IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD%
        ,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD,SAMSUNG_YH92X_PAD%
        ,SAMSUNG_YH820_PAD,XDUOO_X3_PAD}{%
    Switching modes back and forth is done by pressing the
        \opt{SANSA_E200_PAD,SANSA_C200_PAD}{\ButtonRec}%
        \opt{GIGABEAT_S_PAD,SANSA_CLIP_PAD,MROBE100_PAD,IRIVER_H10_PAD,SANSA_FUZEPLUS_PAD}%
            {\ButtonPower}%
        \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}{\ButtonSelect+\ButtonRight}
        \opt{PBELL_VIBE500_PAD}{\ButtonOK+\ButtonLeft}
        \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRec+\ButtonRew}
    and
        \opt{SANSA_E200_PAD,SANSA_C200_PAD}{Long \ButtonRec}%
        \opt{GIGABEAT_S_PAD,SANSA_CLIP_PAD,MROBE100_PAD,IRIVER_H10_PAD,SANSA_FUZEPLUS_PAD}
            {Long \ButtonPower}%
        \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}{\ButtonSelect+\ButtonLeft}
        \opt{PBELL_VIBE500_PAD}{\ButtonOK+\ButtonRight}
        \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRec+\ButtonFF}
        \opt{XDUOO_X3_PAD}{\ButtonOption+\ButtonNext{} or \ButtonOption+\ButtonPrev}
    keys, respectively.%
    }%
    \opt{HAVEREMOTEKEYMAP}{
    Remote %
        \opt{GIGABEAT_RC_PAD}{\ButtonRCDsp / Long \ButtonRCDsp}%
        \opt{MROBE100_RC_PAD}{\ButtonRCMode / Long \ButtonRCMode}
    can also be used to switch modes.%
    }%
    \newline\newline
    The following modes are available:
    \begin{description}

        \item [Multimedia.] This mode lets you control the volume, playback,
        and skips tracks on the host computer. It is equivalent for the
        multimedia keys found on top of some multimedia keyboards.

            \begin{btnmap}
                % Volume up / down
                \opt{SANSA_E200_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonScrollFwd{} / \ButtonScrollBack}
                \opt{SANSA_FUZEPLUS_PAD}{\ButtonUp{} / \ButtonDown;}
                \opt{GIGABEAT_S_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,SANSA_FUZEPLUS_PAD,XDUOO_X3_PAD}
                    {\ButtonVolUp{} / \ButtonVolDown}
                \opt{IRIVER_H10_PAD}{\ButtonScrollUp{} / \ButtonScrollDown}
                \opt{MROBE100_PAD,PBELL_VIBE500_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD%
                    }{\ButtonUp{} / \ButtonDown}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}
                        {\ButtonRCVolUp{} / \ButtonRCVolDown}%
                    &}
                Volume up / down, respectively
                \\

                % Volume mute
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD}{\ButtonSelect}
                \opt{GIGABEAT_S_PAD,SANSA_FUZEPLUS_PAD}{\ButtonSelect; \ButtonBack}
                \opt{IRIVER_H10_PAD}{\ButtonFF}
                \opt{IRIVER_VIBE500_PAD}{\ButtonMenu}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRight}
                \opt{XDUOO_X3_PAD}{\ButtonPower}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCFF}%
                    \opt{MROBE100_RC_PAD}{\ButtonRCHeart}%
                    &}
                Volume mute
                \\

                % Playback play / pause
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD}{\ButtonUp}
                \opt{IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD%
                    ,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD%
                    ,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD,XDUOO_X3_PAD}{\ButtonPlay}
                \opt{GIGABEAT_S_PAD}{\ButtonPlay; \ButtonUp}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{\ButtonRCPlay}%
                    \opt{MROBE100_RC_PAD}{\ButtonRCPlay}%
                    &}
                Play / Pause
                \\

                % Playback stop
                \opt{SANSA_E200_PAD,SANSA_C200_PAD}{\ButtonPower}
                \opt{GIGABEAT_S_PAD}{\ButtonMenu; \ButtonDown}
                \opt{SANSA_CLIP_PAD}{\ButtonHome}
                \opt{IRIVER_H10_PAD}{\ButtonRew; Long \ButtonPlay}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonMenu; Long \ButtonPlay}
                \opt{SANSA_FUZEPLUS_PAD}{Long \ButtonPlay}
                \opt{PBELL_VIBE500_PAD}{\ButtonCancel; Long \ButtonPlay}
                \opt{MROBE100_PAD}{\ButtonDisplay; Long \ButtonPlay}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonLeft}
                \opt{XDUOO_X3_PAD}{\ButtonHome}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCPlay}%
                    \opt{MROBE100_RC_PAD}{\ButtonRCDisplay; Long \ButtonRCPlay}%
                    &}
                Stop
                \\

                % Scan previous track
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,%
                    IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD%
                    ,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonLeft}
                \opt{GIGABEAT_RC_PAD}{\ButtonPrev; \ButtonLeft}%
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRew}
                \opt{XDUOO_X3_PAD}{\ButtonPrev}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{\ButtonRCRew}%
                    &}
                Scan previous track
                \\

                % Scan next track
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD%
                    ,IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD%
                    ,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonRight}
                \opt{GIGABEAT_RC_PAD}{\ButtonNext; \ButtonRight}%
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonFF}
                \opt{XDUOO_X3_PAD}{\ButtonNext}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{\ButtonRCFF}%
                    &}
                Scan next track
                \\
            \end{btnmap}

        \item [Presentation.] This mode lets you control a presentation program
        (e.g. OpenOffice Impress, and some other popular application), making
        the \dap{} a wired remote control device. This mode is can be useful
        for lecturers who does not have a wireless remote control for this
        purpose.

            \begin{btnmap}
                % Slideshow start
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD}{\ButtonUp}
                \opt{GIGABEAT_S_PAD}{\ButtonPlay; \ButtonUp}
                \opt{IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD%
                    ,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD%
                    ,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonPlay}
                \opt{XDUOO_X3_PAD}{\ButtonPower}%
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{\ButtonRCPlay}%
                    &}
                Slideshow start
                \\

                % Slideshow leave
                \opt{SANSA_E200_PAD,SANSA_C200_PAD}{\ButtonPower}
                \opt{GIGABEAT_S_PAD}{Long \ButtonPlay; Long \ButtonUp}
                \opt{SANSA_CLIP_PAD}{\ButtonHome}
                \opt{IRIVER_H10_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}{Long \ButtonPlay}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}{Long \ButtonPlay}
                \opt{MROBE100_PAD}{\ButtonDisplay; Long \ButtonPlay}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRec}
                \opt{XDUOO_X3_PAD}{\ButtonHome}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{Long \ButtonRCPlay}%
                    &}
                Slideshow leave
                \\

                % Slide previous
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonLeft}
                \opt{GIGABEAT_S_PAD}{\ButtonPrev; \ButtonLeft}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRew}
                \opt{XDUOO_X3_PAD}{\ButtonPrev}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                  \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{\ButtonRCRew}%
                  &}
                Slide previous
                \\

                % Slide next
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonRight}
                \opt{GIGABEAT_S_PAD}{\ButtonNext; \ButtonRight}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonFF}
                \opt{XDUOO_X3_PAD}{\ButtonNext}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}{\ButtonRCFF}%
                    &}
                Slide next
                \\

                % Slide first
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {Long \ButtonLeft}
                \opt{GIGABEAT_S_PAD}{Long \ButtonPrev; Long \ButtonLeft}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonRew}
                \opt{XDUOO_X3_PAD}{Long \ButtonPrev}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCRew}%
                    &}
                Slide first
                \\

                % Slide last
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {Long \ButtonRight}
                \opt{GIGABEAT_S_PAD}{Long \ButtonNext; Long \ButtonRight}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonFF}
                \opt{XDUOO_X3_PAD}{Long \ButtonNext}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCFF}%
                    &}
                Slide last
                \\

                % Screen black
                \opt{SANSA_FUZEPLUS_PAD}{\ButtonBottomRight}
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD%
                    ,SANSA_CLIP_PAD}{\ButtonDown}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonLeft}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD}
                    {\ButtonMenu}
                \opt{PBELL_VIBE500_PAD}{\ButtonCancel}
                \opt{XDUOO_X3_PAD}{\ButtonOption}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{\ButtonRCDisplay}%
                    &}
                Black screen
                \\

                % Screen white
                \opt{SANSA_FUZEPLUS_PAD}{Long \ButtonBottomRight}
                \opt{SANSA_E200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD%
                    ,SANSA_CLIP_PAD}{Long \ButtonDown}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonLeft}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD}
                    {Long \ButtonMenu}
                \opt{PBELL_VIBE500_PAD}{\ButtonMenu}
                \opt{XDUOO_X3_PAD}{Long \ButtonOption}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCDisplay}%
                    &}
                White screen
                \\

                % Link previous / next
                \opt{SANSA_E200_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonScrollBack / \ButtonScrollFwd}
                \opt{GIGABEAT_S_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD}
                    {\ButtonVolUp / \ButtonVolDown}
                \opt{IRIVER_H10_PAD}{\ButtonScrollUp / \ButtonScrollDown}
                \opt{MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD,SAMSUNG_YH92X_PAD%
                    ,SAMSUNG_YH820_PAD}
                    {\ButtonUp / \ButtonDown}
                \opt{XDUOO_X3_PAD}{\ButtonVolUp{} / \ButtonVolDown}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}
                        {\ButtonRCVolUp / \ButtonRCVolDown}%
                    &}
                Previous / next link in slide, respectively
                \\

                % Mouse click
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonSelect}
                \opt{GIGABEAT_S_PAD}{\ButtonSelect; \ButtonBack}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRight}
                \opt{PBELL_VIBE500_PAD}{\ButtonOK}
                \opt{XDUOO_X3_PAD}{\ButtonPlay}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCFF}%
                    \opt{MROBE100_RC_PAD}{\ButtonRCHeart}%
                    &}
                Perform a `mouse click' over a link
                \\

                % Mouse over
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD,SANSA_FUZEPLUS_PAD}{Long \ButtonSelect}
                \opt{GIGABEAT_S_PAD}{Long \ButtonSelect; Long \ButtonBack}
                \opt{IRIVER_H10_PAD,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonRight}
                \opt{PBELL_VIBE500_PAD}{Long \ButtonOK}
                \opt{XDUOO_X3_PAD}{Long \ButtonPlay}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCRew}%
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCHeart}%
                    &}
                Perform a `mouse over' over a link
                \\
            \end{btnmap}

        \item [Browser.] This mode lets you control a web browser (e.g.
        Firefox). It uses the \dap{}'s keys to navigate through the web page
        and different tabs, navigate through history, and to control zoom.

            \begin{btnmap}
                % Scroll up / down
                \opt{SANSA_E200_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonScrollBack / \ButtonScrollFwd}
                \opt{SANSA_C200_PAD,SANSA_CLIP_PAD}
                    {\ButtonVolUp / \ButtonVolDown}
                \opt{GIGABEAT_S_PAD}
                    {\ButtonPrev; \ButtonVolUp / \ButtonNext; \ButtonVolDown}
                \opt{IRIVER_H10_PAD}{\ButtonScrollUp / \ButtonScrollDown}
                \opt{MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD,SAMSUNG_YH92X_PAD%
                    ,SAMSUNG_YH820_PAD}
                    {\ButtonUp / \ButtonDown}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}
                        {\ButtonRCVolUp / \ButtonRCVolDown}%
                  &}
                Scroll up / down, respectively
                \\

                % Scroll page up / page down
                \nopt{SANSA_FUZEPLUS_PAD}{
                    \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD}
                        {\ButtonUp / \ButtonDown}
                    \opt{GIGABEAT_S_PAD}{\ButtonUp / \ButtonDown}
                    \opt{IRIVER_H10_PAD}{\ButtonRew / \ButtonFF}
                    \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD}
                        {\ButtonPlay / \ButtonMenu}
                    \opt{PBELL_VIBE500_PAD}{\ButtonOK / \ButtonCancel}
                    \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonLeft / \ButtonRight}
                        &
                    \opt{HAVEREMOTEKEYMAP}{
                        \opt{MROBE100_RC_PAD}{\ButtonRCPlay / \ButtonRCDisplay}%
                        &}
                    Scroll page up / page down, respectively
                    \\
                }

                % Zoom in / out
                \opt{SANSA_FUZEPLUS_PAD}{Long \ButtonBottomRight}
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD}
                    {Long \ButtonUp / Long \ButtonDown}
                \opt{GIGABEAT_S_PAD}{Long \ButtonUp / Long \ButtonDown}
                \opt{IRIVER_H10_PAD}{Long \ButtonRew / Long \ButtonFF}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD,MROBE100_PAD}
                    {Long \ButtonPlay / Long \ButtonMenu}
                \opt{PBELL_VIBE500_PAD}{\ButtonPlay / \ButtonMenu}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonLeft / Long \ButtonRight}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCFF / Long \ButtonRCRew}%
                    \opt{MROBE100_RC_PAD}
                        {Long \ButtonRCPlay / Long \ButtonRCDisplay}%
                    &}
                Zoom in / out, respectively
                \\

                % Zoom reset
                \opt{SANSA_E200_PAD}
                    {Long \ButtonSelect; Long \ButtonUp+\ButtonDown}
                \opt{MROBE100_PAD}
                    {Long \ButtonSelect; Long \ButtonPlay+\ButtonMenu}
                \opt{SANSA_CLIP_PAD,SANSA_C200_PAD}
                    {Long \ButtonSelect; Long \ButtonUp+\ButtonDown}
                \opt{GIGABEAT_S_PAD}
                    {Long \ButtonSelect; Long \ButtonUp+\ButtonDown}
                \opt{IRIVER_H10_PAD}{Long \ButtonRew+\ButtonFF}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {Long \ButtonPlay+\ButtonMenu}
                \opt{PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}{Long \ButtonPlay}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonLeft+\ButtonDown}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCFF+\ButtonRCRew}%
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCHeart}%
                  &}
                Zoom reset
                \\

                % Tab previous / next
                \opt{SANSA_E200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD%
                    ,SANSA_CLIP_PAD,IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD%
                    ,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonLeft / \ButtonRight}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRew / \ButtonFF}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD,MROBE100_RC_PAD}
                        {\ButtonRCRew / \ButtonRCFF}%
                    &}
                Tab previous / next, respectively
                \\

                % Tab close
                \opt{SANSA_FUZEPLUS_PAD}{\ButtonBack}
                \opt{SANSA_E200_PAD,SANSA_C200_PAD}{Long \ButtonPower}
                \opt{GIGABEAT_S_PAD}{Long \ButtonPlay; Long \ButtonBack}
                \opt{SANSA_CLIP_PAD}{Long \ButtonHome}
                \opt{IRIVER_H10_PAD}{Long \ButtonLeft+\ButtonRight}
                \opt{MROBE100_PAD}{Long \ButtonDisplay}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {Long \ButtonSelect+\ButtonMenu}
                \opt{PBELL_VIBE500_PAD}{Long \ButtonCancel}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonPlay}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{Long \ButtonRCPlay}%
                    &}
                Tab close
                \\

                % History back / forward
                \opt{SANSA_E200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD%
                    ,SANSA_CLIP_PAD,IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD%
                    ,IPOD_1G2G_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}
                    {Long \ButtonLeft / Long \ButtonRight}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{Long \ButtonRew / Long \ButtonFF}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{Long \ButtonRCRew / Long \ButtonRCFF}%
                    &}
                History back / forward
                \\

                % View full-screen
                \opt{SANSA_FUZEPLUS_PAD}{Long \ButtonSelect}
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD%
                    ,GIGABEAT_S_PAD,MROBE100_PAD}
                    {\ButtonSelect}
                \opt{IRIVER_H10_PAD}{\ButtonPlay}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {Long \ButtonSelect+\ButtonPlay}
                \opt{PBELL_VIBE500_PAD}{Long \ButtonRec}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRec}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{GIGABEAT_RC_PAD}{\ButtonRCPlay}%
                    \opt{MROBE100_RC_PAD}{\ButtonRCHeart}%
                    &}
                View full-screen toggle
                \\
            \end{btnmap}

        {\opt{usb_hid_mouse}{
        \item [Mouse.] This mode emulates a mouse. Features supported: Mouse
        movement; left and right button clicking; and dragging and dropping.

            \begin{btnmap}
                % Cursor move up / down / left / right
                \opt{SANSA_E200_PAD,GIGABEAT_S_PAD,SANSA_C200_PAD%
                    ,SANSA_CLIP_PAD,MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD%
                    ,SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}
                    {\ButtonUp / \ButtonDown / \ButtonLeft / \ButtonRight}
                \opt{IRIVER_H10_PAD}{\ButtonScrollUp / \ButtonScrollDown /
                    \ButtonLeft / \ButtonRight}
                \opt{IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonMenu / \ButtonPlay / \ButtonLeft / \ButtonRight}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{\ButtonRCPlay / \ButtonRCDisplay /
                        \ButtonRCRew / \ButtonRCFF}%
                    &}
                Cursor move up / down / left / right, respectively
                \\

                % Mouse button left-click
                \opt{SANSA_E200_PAD,SANSA_C200_PAD,SANSA_CLIP_PAD,IPOD_4G_PAD%
                    ,IPOD_3G_PAD,IPOD_1G2G_PAD,SANSA_FUZEPLUS_PAD}
                    {\ButtonSelect}
                \opt{GIGABEAT_S_PAD}{\ButtonSelect; \ButtonBack}
                \opt{IRIVER_H10_PAD}{\ButtonPlay}
                \opt{MROBE100_PAD,PBELL_VIBE500_PAD}{\ButtonMenu}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonRew}
                    &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{\ButtonRCHeart}%
                    &}
                Left mouse button click
                \nopt{IRIVER_H10_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}{
                \\

                % Mouse button right-click
                \opt{SANSA_E200_PAD,SANSA_C200_PAD}{\ButtonPower}
                \opt{GIGABEAT_S_PAD}{\ButtonMenu}
                \opt{SANSA_CLIP_PAD}{\ButtonHome}
                \opt{MROBE100_PAD,PBELL_VIBE500_PAD,SANSA_FUZEPLUS_PAD}{\ButtonPlay}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}{\ButtonFF}
                &
                \opt{HAVEREMOTEKEYMAP}{
                    &}
                Right mouse button click
                }
                \\

                % Mouse wheel scroll up / down
                \opt{SANSA_FUZEPLUS_PAD}
                    {\ButtonBack / \ButtonBottomLeft}
                \opt{SANSA_E200_PAD,IPOD_4G_PAD,IPOD_3G_PAD,IPOD_1G2G_PAD}
                    {\ButtonScrollBack / \ButtonScrollFwd}
                \opt{IRIVER_H10_PAD}{\ButtonRew / \ButtonFF}
                \opt{GIGABEAT_S_PAD}
                    {\ButtonVolUp; \ButtonPrev / \ButtonVolDown; \ButtonNext}
                \opt{SANSA_C200_PAD,SANSA_CLIP_PAD,MROBE100_PAD}
                    {\ButtonVolUp / \ButtonVolDown}
                \opt{PBELL_VIBE500_PAD}
                    {\ButtonOK / \ButtonCancel}
                \opt{SAMSUNG_YH92X_PAD,SAMSUNG_YH820_PAD}
                    {\ButtonRec+\ButtonUp / \ButtonRec+\ButtonDown}
                &
                \opt{HAVEREMOTEKEYMAP}{
                    \opt{MROBE100_RC_PAD}{\ButtonRCVolUp / \ButtonRCVolDown}%
                    &}
                Mouse wheel scroll up / down, respectively
                \\

            \end{btnmap}
    }}
    \end{description}
}
\opt{usb_power}{
  \subsection{USB Mode}
    This controls what happens with the \dap{}'s USB port is connected.
    \setting{Charge Only} and \setting{Mass Storage} will automatically enter
    that mode, and \setting{Ask} will prompt the user each time.
}
\opt{multidrive_usb}{
  \subsection{USB Hide Internal Drive}
    If this option is turned \setting{On}, the internal storage drive will not
    be exposed on the USB Mass Storage Device. This e.g. makes it possible to
    access the card slot from systems that can not handle USB devices with
    multiple drives, such as some car audio systems.
}
