% $Id $ %
The \setting{Theme Settings} menu offers options that you can change to
customize the visual appearance of Rockbox.

\begin{description}
\item[Browse Theme Files.]
  This option will display all the currently installed themes on the \dap{}, 
  press \ActionTreeEnter{} to load the chosen theme and apply it.

  A theme is a configuration file, stored in a specific directory, 
  that typically changes the WPS 
  \opt{HAVE_REMOTE_LCD}{and remote WPS}, font used and on some platforms
  additional information such as background image and text colours.

  There are a number of themes that ship with Rockbox. If none of
  these suit your needs, many more can be downloaded from 
  \opt{iaudiom5}{\url{http://themes.rockbox.org/index.php?target=m5}}%
  \opt{iaudiox5}{\url{http://themes.rockbox.org/index.php?target=x5}}%
  \opt{iaudiom3}{\url{http://themes.rockbox.org/index.php?target=m3}}%
  \opt{iriverh100}{\url{http://themes.rockbox.org/index.php?target=h100}}%
  \opt{iriverh300}{\url{http://themes.rockbox.org/index.php?target=h300}}%
  \opt{iriverh10_5gb}{\url{http://themes.rockbox.org/index.php?target=h10_5gb}}%
  \opt{iriverh10}{\url{http://themes.rockbox.org/index.php?target=h10}}%
  \opt{ipod1g2g}{\url{http://themes.rockbox.org/index.php?target=ipod1g2g}}%
  \opt{ipod3g}{\url{http://themes.rockbox.org/index.php?target=ipod3g}}%
  \opt{ipod4g}{\url{http://themes.rockbox.org/index.php?target=ipod4g}}%
  \opt{ipodcolor}{\url{http://themes.rockbox.org/index.php?target=ipodcolor}}%
  \opt{ipodvideo}{\url{http://themes.rockbox.org/index.php?target=ipodvideo}}%
  \opt{ipodmini}{\url{http://themes.rockbox.org/index.php?target=ipodmini}}%
  \opt{ipodnano}{\url{http://themes.rockbox.org/index.php?target=ipodnano}}%
  \opt{ipodnano2g}{\url{http://themes.rockbox.org/index.php?target=ipodnano2g}}%
  \opt{e200}{\url{http://themes.rockbox.org/index.php?target=e200}}%
  \opt{e200v2}{\url{http://themes.rockbox.org/index.php?target=e200v2}}%
  \opt{c200}{\url{http://themes.rockbox.org/index.php?target=c200}}%
  \opt{gigabeatf}{\url{http://themes.rockbox.org/index.php?target=gigabeatf}}%
  \opt{gigabeats}{\url{http://themes.rockbox.org/index.php?target=gigabeats}}%
  \opt{mrobe100}{\url{http://themes.rockbox.org/index.php?target=mrobe100}}%
  \opt{vibe500}{\url{http://themes.rockbox.org/index.php?target=vibe500}}%
  \opt{fuzeplus}{\url{http://themes.rockbox.org/index.php?target=sansafuzeplus}}%
  \opt{samsungyh820}{\url{http://themes.rockbox.org/index.php?target=samsungyh820}}%
  \opt{samsungyh920}{\url{http://themes.rockbox.org/index.php?target=samsungyh920}}%
  \opt{samsungyh925}{\url{http://themes.rockbox.org/index.php?target=samsungyh925}}%
  .

  \note{Themes do not have to be purely visual. It is quite possible to create
    a theme that switches between audio configurations for use in the car, with
    headphones and when connected to an external amplifier. See
    \reference{ref:CreateYourOwnWPS} for more details.}

  \item[Font.]
    Browse the installed fonts on your \dap{}. Selecting one will activate it.
    See \reference{ref:Loadingfonts} for further details about fonts.

\item[While Playing Screen.]
  Opens the \setting{File Browser} in the \fname{/.rockbox/wps} directory and
  displays all \fname{.wps} files. Selecting one will activate it,
  \ActionStdCancel{} will exit back to the menu. For further information
  about the WPS see \reference{ref:WPS}. For information about editing
  a .wps file see \reference{ref:ConfiguringtheWPS}.

\opt{HAVE_REMOTE_LCD}{
  \item[Remote While Playing Screen.]
    Opens the \setting{File Browser} in the \fname{/.rockbox/wps} directory and
    displays all \fname{.rwps} files. Selecting one will activate it, stop will
    exit back to the menu.
    \note{
      A \fname{.rwps} file is a special \fname{.wps} file for the remote
      display.
    }
}

\item[Show Icons.]
  Rockbox has the ability to display an icon to the left of the file
  in the \setting{File Browser}. For details of these icons, see
  \reference{ref:Supportedfileformats}.
  These icons can also be customised. See the \wikilink{IconSets}
  and \wikilink{CustomIcons} Wiki pages for details.

\opt{lcd_non-mono}{%
  \item[Clear Backdrop.]
    Rockbox allows you to select bitmap pictures to use as backdrops,
    see \reference{ref:LoadingBackdrops} for further information.
    This option allows you to clear the backdrops that you set.
}
%
\item[Status/Scrollbar.]
  Settings related to on screen status display and the scrollbar.
  \begin{description}
  \item[Scroll Bar.] Allows you to choose where the vertical scroll bar
    should appear.
  \item[Scroll Bar Width.] Allows you to choose the width of the
    scroll bar (in pixels).  Default value is 6.
  \item[Status Bar.] Allows you to choose where to display the 
    statusbar\opt{remote}{ on the main display}. 
  \opt{remote}{
    \item[Remote Status Bar.] Allows you to choose where to display the 
    statusbar on the remote display.
  }
  \item[Volume Display.] Controls whether the volume is displayed as a
    graphic or a numeric value on the Status Bar. If you select a numeric
    display, volume is displayed in decibels.  See \reference{ref:volume}
    for more on the volume setting.
  \item[Battery Display.] Controls whether the battery charge status is
    displayed as a graphic or numerical percentage value on the Status Bar.
  \end{description}
%
\item[Line Selector Type.]
  This option allows you to select which type of line selector to use.
  \begin{description}
    \item[Pointer.]
      A small arrow to the left of the menu text.
    \item[Bar (inverse).]
      A bar with inverted foreground and background colour.
\opt{lcd_color}{
    \item[Bar (Solid Colour).]
      A bar with a solid colour, the colour is set in the \setting{Colours}
      submenu.
    \item[Bar (Gradient Colour).]
      A bar with a colour gradient, the colours are set in the \setting{Colours}
      submenu.
}
  \end{description}

\opt{lcd_color}{
  \item[Colours.]
    The options in this menu sets the colours for visual elements in Rockbox.
    \begin{description}
    \item[Line Selector Colours.]
      These options sets the colours for the line selector bars.
      \begin{description}
        \item[Primary Colour.]
          Set the primary colour used for the gradient line selector bar and the
          colour used for the solid color line selector bar.
        \item[Secondary Colour.]
          Set the secondary colour used for the gradient line selector bar.
        \item[Text Colour.]
          Set the colour of the selected text when using the solid colour or the
          gradient colour line selection bars.
      \end{description}

    \item[Background Colour.]
      Sets the background colour for the display.
    \item[Foreground Colour.]
      Sets the colour used for text and icons.
    \item[Reset Colours.]
      Resets the LCD display to Rockbox's default colours.
    \end{description}
}% lcd_color
\end{description}
