% $Id$ %
\appendix

\input{appendix/file_formats.tex}

\input{appendix/wps_tags.tex}

\input{appendix/config_file_options.tex}

\chapter{User feedback}\label{sec:feedback}
\section{Bug reports}
If you experience inappropriate performance from any supported feature,
please file a bug report on our web page. Do not report missing
features as bugs, instead file them as feature ideas (see below).

For open bug reports refer to
\url{http://www.rockbox.org/tracker/index.php?type=2}

\subsection{Rules for submitting new bug reports}

\begin{enumerate}
\item  Check that the bug has not already been reported
\item  Always include the following information in your bug report:
\end{enumerate}

\begin{itemize}
\item  Which exact \dap{} you have.
\item  Which exact Rockbox version you are using
(Menu{}-{\textgreater}Info {}-{\textgreater} Version)
\item  A step{}-by{}-step description of what you did and what happened
\item  Whether the problem is repeatable or a one{}-time occurrence
\item  All relevant data regarding the problem, such as playlists, MP3
files etc. (IMPORTANT!) 
\end{itemize}

\section{Feature ideas}
To suggest an idea for a feature or to read those made by others, see
\url{http://forums.rockbox.org/index.php?board=49.0}.  Please keep in
mind that this forum is for the discussion of feature ideas - they are not
 requests and there is no guarantee they will be acted upon.

\subsection{Rules for submitting a new feature idea}

\begin{enumerate}
\item Check that the feature has not already been requested. 
  Duplicates are really boring!
\item Check that the feature has not already been implemented. 
  Download the latest current/daily build and/or search the mail list archive.
\item Check that the feature is possible to implement (see \reference{ref:NODO}).
\end{enumerate}

\subsection{\label{ref:NODO}Features we will not implement}
This is a list of Feature Requests we get repeatedly that we simply
cannot do. View it as the opposite of a TODO!

\begin{itemize}
\opt{archos}{
\item Record to WAV (uncompressed) or MP3pro format!\\
The recording hardware (the MAS) does not allow us to do this
\item Crossfade between tracks!\\
  Crossfading would require two mp3 decoders, and we only have one. 
  This is not possible.
\item Support MP3pro, WMA or other sound format playback!\\
  The mp3{}-decoding hardware can only play MP3. We cannot make it play other 
  sound formats.
\item  Converting OGG $\rightarrow$ MP3 \\
  The mp3{}-decoding hardware cannot decode OGG. It can be reprogrammed, but 
  there is too little memory for OGG and we have no documentation on how to 
  program the MAS' DSP. Doing the conversion with the CPU is impossible, since 
  a 12MHz SH1 is far too slow for this daunting task.
\item Archos Multimedia support!\\
  The Archos Multimedia is a completely different beast. It is an entirely 
  different architecture, different CPU and upgrading the software is done 
  a completely different way. We do not wish to venture into this.  Others 
  may do so. We will not.
\item Multi{}-band (or graphic) equaliser\\
  We cannot access information for that kind of visualisation from the MP3 
  decoding hardware.
\item CBR recording!\\
  The MP3 encoding hardware does not allow this.
\item Change tempo of a song without changing pitch!\\
  The MP3 decoding hardware does not allow this.
\item Graphic frequency (spectrum analyser!)\\
  We cannot access the audio waveform from the MP3 decoder so we cannot analyse 
  it. Even if we had access to it, the CPU would probably be too slow to 
  perform the analysis anyway.
\item Cool sound effects!\\
  Adding new sound effects requires reprogramming the MAS chip, and we cannot 
  do that. The MAS chip is programmable, but we have no access to the chip 
  documentation.
}
\nopt{h300,x5}{
\item Interfacing with other USB devices (like cameras) or 2 player games over USB\\
  The USB system demands that there is a master that talks to a slave. The
  \dap{} can only serve as a slave, as most other USB devices such as
  cameras can. Thus, without a master no communication between the slaves
  can take place. If that is not enough, we have no ways of actually
  controlling the communication performed over USB since the USB circuit
  in the \dap{} is strictly made for disk{}-access and does not allow us
  to play with it the way we'd need for any good communication to work.
}
\item Support other file systems than FAT32 (like NTFS or ext2 or whatever)!\\
  No.
  \opt{archos}{Rockbox needs to support FAT32 since it can only start off a FAT32
  partition (since that is the only way the ROM can load it), and adding}%
  support for more file systems will just take away valuable ram for
  unnecessary features. You can partition your \dap{} fine, just make sure
  the first one is FAT32 and then make the other ones whatever file system
  you want. Just do not expect Rockbox to understand them.
\item Add scandisk{}-like features!\\
  It would be a very slow operation that would drain the batteries and
  take a lot of useful ram for something that is much better and faster
  done when connected to a host computer.
\end{itemize}

\chapter{Changelog}
\section{What is new since v2.5?}
Changes in version 2.5

\chapter{Credits}
People that have contributed to the project, one way or another. Friends!
%
\begin{multicols}{2}
\noindent\textsc{\small{\input{CREDITS.tex}}}
\end{multicols}

\chapter{Licenses}

\section{GNU Free Documentation License}
\input{appendix/fdl.tex}
\newpage
\section{The GNU General Public License}
\input{appendix/gpl-2.0.tex}
